A Type System for String Sanitation\\Implemented Inside a Python

### 2014-08-05 sanitation-psp14/sanitation-psp14-short.tex
elements can't be iso

\begin{lem}{Substitution Correspondence.} \label{thm:substcorrespondence}
If $s_1 \in \lang{r_1}$ and $s_2 \in \lang{r_2}$ then $\lsubst{r}{s_1}{s_2} \in \lang{\lreplace{r}{r_1}{r_2}}$.
\end{lem}
\begin{proof}
The proof proceeds by structural induction on $r$.
The base case ($r=\alpha, \alpha \in \Sigma$) is trivial.
The choice and sequential cases require lemma 1, and prove a more general property that $\lsubst{r}{s_1}{s_2} \in \lang{r'}$ for some $r'$ isomorphic to $\lreplace{r}{r_1}{r_2}$.
The closure case follows from the induction hypothesis applied to any $n$-unwinding.

>>>>

\begin{lem}{Substitution Correspondence.} \label{thm:substcorrespondence}
If $s_1 \in \lang{r_1}$ and $s_2 \in \lang{r_2}$ then $\lsubst{r}{s_1}{s_2} \in \lang{\lreplace{r}{r_1}{r_2}}$.
\end{lem}
\begin{proof}
The proof proceeds by structural induction on $r$.
The base case ($r=\alpha, \alpha \in \Sigma$) is trivial.
The choice and sequential cases require lemma 1, and prove a more general property that $\lsubst{r}{s_1}{s_2} \in \lang{r'}$ for some $r'$ equivalent to $\lreplace{r}{r_1}{r_2}$.
The closure case follows from the induction hypothesis applied to any $n$-unwinding.
